\documentclass[letterpaper, 10pt]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[hidelinks]{hyperref} % Required for hyperlinks
\usepackage[top=0.5in, bottom=0.5in, left=0.7in, right=0.7in]{geometry} % Page margins
\pagestyle{empty} % No page numbers
\begin{document}
%----------HEADING----------
\begin{center}
 \textbf{\LARGE Gil Taeho} \\ \vspace{2pt}
 \href{mailto:yourmail@skku.edu}{\underline{gth4810@skku.edu}} $|$
 \href{https://github.com/GilTaeho}{\underline{github.com/GilTaeho}}
\end{center}
%-----------TECHNICAL SKILLS-----------
\section*{Technical Skills}
\hrule
\vspace{4pt}
\begin{itemize}
 % \item[] : same as \item but with no bullet point ([] replaces the bullet symbol with nothing)
 \item[] \textbf{Programming}: Python, C, JavaScript % List your programming languages
 \item[] \textbf{Frameworks \& Tools}: Git, GitHub, Docker, Bash, Jupyter % List your frameworks and tools
 \item[] \textbf{Languages}: Korean(native), English(Advanced) % List your spoken languages
\end{itemize}
%-----------EXPERIENCE-----------
\section*{Experience}
\hrule
\vspace{4pt}
\begin{itemize}
 \item[]
 % \hfill : fills the remaining horizontal space, pushing text to the right
 \textbf{English Translator(military service)} \hfill Aug. 2023 -- Jan. 2025 \\ % e.g. Mar. 2024 -- Present
 \textit{Korea Armed Forces Athletic Corps} \hfill \textit{Mungyeong, Korea}
 \begin{itemize}
 \item Served as an interpreter on overseas dispatches to international sports competitions in the Netherlands and Thailand.
 \item Supported the planning and operation of a large-scale international sports event hosted by the unit.
 \end{itemize}
 \item[]
 \textbf{Project Tech Leader, SMARCLE} \hfill Dec. 2022 -- Mar. 2023 \\ % e.g. Mar. 2024 -- Present
 \textit{SJU AI Club} \hfill \textit{Seoul, Korea}
 \begin{itemize}
 \item Participated in a club project team focused on applied deep learning.
 \item Took charge of software implementation and collaborated with team members through weekly meetings.
 \end{itemize}
\end{itemize}
%-----------SELECTED PROJECTS-----------
% Include: project name, brief description, and your role
\section*{Selected Projects}
\hrule
\vspace{4pt}
\begin{itemize}
    \item[]
    \textbf{Graph DB Traversal with CPU Scheduling} \hfill 2026 -- Present \\
    \textit{Course Research Project, SKKU} \hfill \textit{(Ongoing)}
    \begin{itemize}
        \item Investigating an extension of Dijkstra's algorithm for multi-hop traversal in graph databases.
        \item Applying a Multi-Level Feedback Queue (MLFQ) scheduling strategy to mitigate hallucination issues in multi-hop reasoning.
        \item Role: designing the algorithm and implementing the prototype; results pending.
    \end{itemize}
    \item[]
    \textbf{Facial Expression Recognition with CNN} \hfill Dec. 2022 -- Mar. 2023 \\
    \textit{SMARCLE Club Project, SJU}
    \begin{itemize}
        \item Built a Convolutional Neural Network to classify facial expressions from image inputs.
        \item Implemented the model training and inference pipeline in Python.
        \item Role: developer responsible for model architecture and training.
    \end{itemize}
\end{itemize}
%-----------HONORS & AWARDS-----------
% Include: awards, certifications, or honors you have
\section*{Honors \& Awards}
\hrule
\vspace{4pt}
\begin{itemize}
    \item \textbf{TOEIC 945} \hfill 2025
    \item \textbf{Academic Excellence Scholarship (2 times)} \hfill Sejong University
    \item \textbf{Excellence Award, Major Mentoring Program} \hfill Sejong University
    \item \textbf{Class 1 Ordinary Driver's License}
\end{itemize}
%-----------EDUCATION-----------
% Include: university name, degree, major, relevant courses, academic accomplishments, etc
\section*{Education}
\hrule
\vspace{4pt}

\begin{itemize}
    \item[]
    \textbf{Sungkyunkwan University (SKKU)} \hfill Mar. 2026 -- Present \\
    \textit{B.S. in Software, College of Software} \hfill \textit{Suwon, Korea}
    \item[]
    \textbf{Sejong University} \hfill Mar. 2022 -- Feb. 2026 \\
    \textit{B.S. in Unmanned Vehicle Engineering, School of Intelligent Mechatronics Engineering} \hfill \textit{Seoul, Korea}
\end{itemize}
%-------------------------------------------
\end{document}